---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  cache = TRUE
)
```

# pisaUSA15

The goal of pisaUSA15 is to make it easy to access the student assessment and questionnaire, teacher questionnaire, and school questionnaire data from the 2015 [PISA assessment](http://www.oecd.org/pisa/data/). The 2015 dataset includes responses from more than 500,000 students, while this package includes the almost 6,000 responses associated with students in the USA. 

## Installation

You can install pisaUSA15 from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jrosen48/pisaUSA15")
```

## Example

Here is how to load the four datasets:

```{r example}
library(pisaUSA15)
library(tibble)

stu_assess
stu_quest
tch_quest
sch_quest
```

## Merging datasets

Joining the student assessment and student questionnaire:

```{r joining-student-data}
library(dplyr)
left_join(stu_assess, stu_quest, by = "CNTSTUID")
```

Joining student-level data (either the student assessment or student questionnaire) with teacher or school questionnaires:

```{r joining-student-and-teacher-or-school-data}
left_join(stu_quest, tch_quest, by = "SCHID")
left_join(stu_assess, tch_quest, by = "SCHID")
```

Joining teacher and school questionnaires:

```{r}
left_join(tch_quest, sch_quest, by = "SCHID")
```
